A sensor grid approach for large scale acoustic monitoring

### 2017-06-16 paper/article.tex
sketch abstract

\address{felix.gontier@reseau.eseo.fr\\mathieu.lagrange@cnrs.fr}

@@

@@

\begin{keyword}
%% keywords here, in the form: keyword \sep keyword

>>>>

\address{felix.gontier@reseau.eseo.fr \\ mathieu.lagrange@cnrs.fr}

@@

The acoustic environment represents both societal and environmental concerns, in particular for cities that are subjected to a multitude of noise sources and that count de facto numerous exposed people.

In this context, monitoring the acoustic environnment in urban but also rural or wilderness areas is an important matter. Fostering on the recent development of low cost hardware acoustic sensors, we propose to using a sensor grid approach.

audio sensing

audio encoding

@@

\begin{keyword}

acoustic monitoring \sep soundscape assessment \sep
%% keywords here, in the form: keyword \sep keyword
